\documentclass{resume}

% personal info header
\name{Bryan}{Hitchcock}
\email{bryanhitc@gmail.com}
\social[linkedin][linkedin.com/in/bryan-hitchcock]{bryan-hitchcock}
\social[github][github.com/BryanHitchcock]{BryanHitchcock}

\begin{document}
\vspace*{-10mm}
\maketitle
\vspace*{-10mm}

\section{Education}
\cvitemwithcomment{}{\textbf{Michigan State University}}{\normalsize\textnormal{Aug 2016 - May 2020}}
\cvitem{}{\textit{Computer Science, B.S., GPA: 3.78/4.00, Major GPA: 3.92/4.00}}
\cvitem{}{\textit{\underline{Honors:} Engineering College Dean's List}}
% \begin{itemize}
%     \item \cvitem{}{\textit{\underline{Honors:} Engineering College Dean's List}}
%     \item \cvitem{}{\textit{\underline{Electives:} Advanced C++ \textbf{(6 students invited)}, Algorithm Engineering, Parallel Computing (HPC), Databases, Compilers and Interpreters, Operating Systems, Computer Networks, Biometrics and Pattern Recognition}}
% \end{itemize}

% \section{Experience}
% \cvitemwithcomment{}{\textbf{BS\&A Software}: Software Engineer, Intern}{\normalsize\textnormal{May 2019 - Aug 2019}}
% \cvitem{}{Designed and created an internal Angular web app used by all \textasciitilde{180} employees to facilitate collaboration, saving \textasciitilde{\$4,000/month} in Trello costs. Designed back end RESTful API and web socket infrastructure written in C\# ASP.NET Core.}

\section{Experience}
\cvitemwithcomment{}{\textbf{BS\&A Software}: Software Engineer, Intern}{\normalsize\textnormal{May 2019 - Aug 2019}}
\begin{itemize}
    \item \cvitem{}{Designed and created an internal TypeScript Angular web app used by all \textasciitilde{180} employees to facilitate collaboration, saving \textasciitilde{\$4,000/month} in Trello costs.}
    \item \cvitem{}{Designed back end RESTful API and web socket infrastructure written in C\# ASP.NET Core.}
\end{itemize}

\vspace{2mm}
\cvitemwithcomment{}{\textbf{Teaching Assistant}: CSE 450 - Compilers and Interpreters}{\normalsize\textnormal{Aug 2019 - Dec 2019}}
\begin{itemize}
    \item \cvitem{}{Assisted students with designing and implementing their compilers that staged through lexical, syntactic, and semantic analysis, intermediate language generation, optimization, and target code generation.}
\end{itemize}

% \vspace{2mm}
% \cvitemwithcomment{}{\textbf{Teaching Assistant}: CSE XXX - Course Name}{\normalsize\textnormal{Jan 2020 - May 2020}}

\vspace{-2mm}
\section{Projects}
\cvitemwithcomment{}{\href{http://github.com/BryanHitchcock/course-sniper}{\textbf{Course Sniper}}}{\normalsize\textnormal{Apr 2019 - May 2019}}
% \cvitem{}{C\# WPF desktop application and IoT console application that automatically enrolls in planned courses whenever there's an available spot. Deployed IoT application targeting Michigan State University's scheduling system on a Raspberry Pi.}
\begin{itemize}
    \item \cvitem{}{C\# WPF desktop application and IoT console application that automatically enrolls in planned courses whenever there's an available spot.}
    \item \cvitem{}{Deployed IoT application targeting Michigan State University's scheduling system on a Raspberry Pi.}
\end{itemize}

\vspace{2mm}
\cvitemwithcomment{}{\textbf{LOLCode Compiler}}{\normalsize\textnormal{Aug 2018 - Dec 2018}}
% \cvitem{}{Compiler written in Python for a language called LOLCode. Stages through lexical, syntactic, and semantic analysis, intermediate language generation, optimization, and target code generation. 100\% code coverage via pytest.}
\begin{itemize}
    \item \cvitem{}{Compiler written in Python for a language called LOLCode.}
    \item \cvitem{}{Stages through lexical, syntactic, and semantic analysis, intermediate language generation, optimization, and target code generation.}
\end{itemize}

\vspace{2mm}
\cvitemwithcomment{}{\textbf{SQLite Database}}{\normalsize\textnormal{Jan 2019 - May 2019}}
% \cvitem{}{Python project that lexes, parses, and interprets SQL for a SQLite-like database. Implementation includes joins, transactions, multiple connections, lock management, custom aggregate functions, collations, views, etc. 100\% code coverage via pytest.}
\begin{itemize}
    \item \cvitem{}{Python project that lexes, parses, and interprets SQL for a SQLite-like database.}
    \item \cvitem{}{Implementation includes joins, transactions, multiple connections, lock management, custom aggregate functions, collations, views, etc.}
\end{itemize}

\vspace{2mm}
\cvitemwithcomment{}{\href{http://github.com/BryanHitchcock/lcu-sharp}{\textbf{LCUSharp}}}{\normalsize\textnormal{Dec 2018 - Jan 2019}}
% \cvitem{}{API wrapper written in C\# for the League of Legends client that interfaces with it directly via http requests and web sockets.}
\begin{itemize}
    \item \cvitem{}{API wrapper written in C\# for the League of Legends client that interfaces with it directly via http requests and web sockets.}
\end{itemize}

\vspace{-2mm}
\section{Skills}
\begin{itemize}
    \item \cvitem{Languages}{Python, C\#, C/C++, JavaScript/TypeScript, Java, SQL, \textit{Rust}, \textit{CUDA}}{}
    \item \cvitem{Libraries \& Frameworks}{OpenMP, MPI, Angular, VueJS, Flask, ASP.NET Core, Entity Framework Core}{}
    \item \cvitem{Tools \& Technologies}{Git, Docker, Unit/Functional/Integration Testing, Amazon Web Services, Microsoft Azure, Visual Studio 2019, Visual Studio Code}{}
\end{itemize}

\vspace{-2mm}
\section{Course Electives}
\vspace{-3mm}
\begin{multicols}{2}
\begin{itemize}
    \item \cvitem{CSE 402}{Biometrics and Pattern Recognition}
    \item \cvitem{CSE 410}{Operating Systems}
    \item \cvitem{CSE 415}{Parallel Computing (HPC)}
    \item \cvitem{CSE 422}{Computer Networks}
    \item \cvitem{CSE 431}{Algorithm Engineering}
    \item \cvitem{CSE 450}{Compilers and Interpreters}
    \item \cvitem{CSE 480}{Databases}
    \item \cvitem{CSE 491}{Advanced C++ \textbf{(6 students invited)}}
\end{itemize}
\end{multicols}
\end{document}
